
### Top line Journey Results {.tabset}

All major journeys across the National Trust website areas.   

The pre launch baseline is created from **`r format(baseline_pre_date_range[1], "%b %d")` to `r format(baseline_pre_date_range[2], "%b %d")`**
This shows the average daily visits to the journey in the old website.

The post launch baseline is created from the available data since launch **`r format(baseline_post_start_date, "%b %d")` to `r format(last_valid_date, "%b %d")`**.  

This shows the average daily visits to the journey in the new website.   

This is currently **`r days_since_launch`** full days since the launch on **`r format(launch_date_start, "%b %d")`**.

#### All Journeys


```{r all_journeys_before_after, echo=FALSE, fig.height=9, fig.width=12, message=FALSE, warning=FALSE}

get_journey_plot(all_journeys_before_after_plot)

```


#### New Site

Journeys that only exist in the new CMS. Due to their being no backward comparison, these journeys are monitored by using a previous week performance as their baseline measures.


```{r all_post_only_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_post_only_journey_plot(post_only_plot)

```


#### Landing Pages

First pages of a user journey. 


```{r all_landing_page_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_landing_page_journeys)

```


#### Device

Journeys from specfic devices or operating systems.

```{r all_device_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_device_journeys)

```


#### Commercial

Any journey that contains a commercial journey.

```{r all_commercial_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_commercial_journeys)

```


#### Home Page

Journeys from the home page onward to other significant areas of the website.

```{r all_top_level_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_top_level_journeys)

```

#### Property

Journeys to a NT property page.

```{r all_property_page_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_property_page_journeys)

```

#### Discovery

Journeys categorised as a research or discovery journey.

```{r all_discovery_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_discovery_journeys)

```


#### Browser

Journeys categorised as a browser specific journey across the entire website.

```{r all_browser_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_browser_journeys)

```



#### Baseline Table


```{r baseline_journeys_table, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}
  datatable(baseline_flex_table, rownames = FALSE, colnames = c('Journey Name' = 1, 
                                  'Type' = 2,
                                  'Avg. Visits' = 3,
                                  '% New Visits' = 4,
                                  '% Repeat Visits' = 5,
                                  'Avg. New Visits' = 6,
                                  'Avg. Repeat Visits' = 7), filter = 'none')
```

### {.unlisted .unnumbered}
