
### Top line Journey Results {.tabset}

#### All Journeys

All major journeys across the National Trust website areas.

```{r all_journeys_before_after, echo=FALSE, fig.height=9, fig.width=12, message=FALSE, warning=FALSE}

get_journey_plot(all_journeys_before_after_plot)

```
#### Landing Pages

First pages of a user journey. 

```{r all_landing_page_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_landing_page_journeys)

```


#### Device

Journeys from specfic devices or operating systems.

```{r all_device_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_device_journeys)

```


#### Commercial

Any journey that contains a commercial journey.

```{r all_commercial_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_commercial_journeys)

```


#### Top Level

Journeys from the home page onward to other significant areas of the website.

```{r all_top_level_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_top_level_journeys)

```

#### Property Pages

Journeys to a NT property page.

```{r all_property_page_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_property_page_journeys)

```

#### Discovery

Journeys categorised as a research or discovery journey.

```{r all_discovery_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_discovery_journeys)

```

### {.unlisted .unnumbered}
