
### Top line Journey Results {.tabset}

All major journeys across the National Trust website areas.   

The pre launch baseline is created from **`r format(baseline_pre_date_range[1], "%b %d")` to `r format(baseline_pre_date_range[2], "%b %d")`**
This shows the average daily visits to the journey in the old website.

The post launch baseline is created from the available data since launch **`r format(baseline_post_start_date, "%b %d")` to `r format(last_valid_date, "%b %d")`**.  

This shows the average daily visits to the journey in the new website.   

This is currently **`r days_since_launch`** full days since the launch on **`r format(launch_date_start, "%b %d")`**.

#### All Journeys


```{r all_journeys_before_after, echo=FALSE, fig.height=12, fig.width=12, message=FALSE, warning=FALSE}

get_journey_plot(all_journeys_before_after_plot, "Visits")

```


#### New Site

Journeys that only exist in the new CMS. Due to their being no backward comparison, these journeys are monitored by using a previous week performance as their baseline measures.

```{r all_post_only_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_post_only_journey_plot(post_only_plot)

```


#### Significant

Journeys with the most significant changes in their journey data. This is based on the equal number of days in the post and pre period.  
E.g. 15 days after launch will also include the 15 days prior to launch.  


```{r all_journeys_signifcant, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_journeys_significant,"Visits")

```



#### Landing Pages

First pages of a user journey. 


```{r all_landing_page_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_landing_page_journeys,"Visits")

```


#### Device

Journeys from specific devices or operating systems.

```{r all_device_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_device_journeys, "Visits")

```


#### Commercial

Any journey that contains a commercial journey.

```{r all_commercial_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_commercial_journeys, "Visits")

```


#### Home Page

Journeys from the home page onward to other significant areas of the website.

```{r all_top_level_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_top_level_journeys, "Visits")

```

#### Discovery

Journeys categorised as a research or discovery journey.

```{r all_discovery_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_discovery_journeys, "Visits")

```


#### Help

Journeys categorised as a help centre activity.

```{r all_browser_journeys, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}

get_journey_plot(all_help_journeys, "Visits")

```



#### Baseline Table


```{r baseline_journeys_table, echo=FALSE, fig.height=7, fig.width=9, message=FALSE, warning=FALSE}
  datatable(baseline_flex_table, rownames = FALSE, colnames = c('Journey Name' = 1, 
                                  'Type' = 2,
                                  'Avg. Visits' = 3,
                                  '% New Visits' = 4,
                                  '% Repeat Visits' = 5,
                                  'Avg. New Visits' = 6,
                                  'Avg. Repeat Visits' = 7), filter = 'none')
```

### {.unlisted .unnumbered}
