
### Membership {.tabset}

Insights:

#### Summary

```{r insights_membership, echo=FALSE}
# min
paste0('The lowest amount of Visits was ', journey.insight$min.Visits, ' observed on ', format(journey.insight$min.Visits.Date.Name, "%d %b"), '.')
# average
paste0('It was ', journey.insight$min.avg.diff, '% less than the average of ', journey.insight$avg.Visits, '.')
# max
paste0('During this period, the amount of Visits peaked at ', journey.insight$max.Visits, ' on ', format(journey.insight$max.Visits.Date.Name, "%d %b"), '.')
# spike
paste0('The most recent spike in Visits increased notably on ', format(journey.spike.most.recent.date$Day, "%d %b"), 
       ' where a peak of ',journey.spike.most.recent.date$Visits, ' Visits was observed. This was 1 Standard Deviation above the mean.')
```



#### Funnels
**Week on Week performance**

Membership funnel completions through the journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r membership_funnel_pre_post, echo=FALSE}
#library(plotly)
  membership_pre_post_funnel 

```

**Week on Week performance**

Membership funnel completions through the checkout journey, this variation includes the Join Us page prior to the start of the Membership funnel journey.  
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  


```{r membership_funnel_pre_start,fig.align='center',echo=FALSE}

membership_pre_post_start_funnel

```


#### Sales & Revenue




#### Metrics
```{r membership_metrics}

```


#### Flows

Membership conversions by Channel. Start: **`r previous_week_7_start` to `r previous_week_7_end`**. 

```{r membership_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}
membership_conv_scatter_plot  
membership_conv_flow_plot
```


#### Change Point {.unlisted .unnumbered}

This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_membership@cpts[1]`**.

```{r membership_changepoints, echo=FALSE, fig.height=5, fig.width=7}

plot(fit_changepoint_membership)

```

### {.unlisted .unnumbered}


### Renewals {.tabset}

Insights:

#### Summary


#### Funnels

**Week on Week performance**

Renewal funnel completions through the journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r renew_funnel_pre, fig.align='center',echo=FALSE}

renew_pre_post_funnel

```

**Week on Week performance**

Renewal funnel completions through the checkout journey, this variation includes the Join or Renew page traffic prior to the start of the funnel journey.  
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r renew_funnel_pre_start,fig.align='center',echo=FALSE}

renew_pre_post_start_funnel

```


#### Sales & Revenue




#### Metrics



#### Flows
Renewals conversions by Channel. Start: **`r previous_week_7_start` to `r previous_week_7_end`**. 

```{r renewals_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}

membership_renewals_conv_scatter_plot  
membership_renewals_conv_flow_plot

```

#### Change Point {.unlisted .unnumbered}


This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_renew@cpts[1]`**.


```{r renew_changepoints, echo=FALSE, fig.height=5, fig.width=7}


plot(fit_changepoint_renew)


```

### {.unlisted .unnumbered}


### Holidays {.tabset}

Insights:

#### Summary


#### Funnels

**Week on Week performance**

Holidays funnel completions through the journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  
 
```{r holidays_funnel_pre, fig.align='center',echo=FALSE}

holidays_pre_post_funnel

```

**Week on Week performance**

Holidays funnel completions through the checkout journey, this variation includes the any page in the Holidays section prior to the start of the funnel journey. 
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  


```{r holidays_funnel_post, fig.align='center',echo=FALSE}

holidays_pre_post_start_funnel
```


#### Sales & Revenue




#### Metrics



#### Flows
```{r holidays_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}

holidays_conv_scatter_plot  
holidays_conv_flow_plot

```


#### Change Point {.unlisted .unnumbered}

This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_holidays@cpts[1]`**.

```{r holidays_changepoints, echo=FALSE, fig.height=5, fig.width=7}

plot(fit_changepoint_holidays)

```


### {.unlisted .unnumbered}


### Shop {.tabset}

Insights:

[Min] The lowest amount of Shop - Order Step 4 - Order Confirmation (Serialized) (ev182) was 15, which occurred on Feb. 3rd and was 84% less than the average of 92.

#### Summary


```{r shop_summary, fig.align='center', fig.height=5, fig.width=7, ECHO=FALSE}
head(mtcars)
```


#### Funnels

**Week on Week performance**

Shop funnel completions through the checkout journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r shop_funnel_pre, fig.align='center',echo=FALSE}

shop_pre_post_funnel

```

**Week on Week performance**

Shop funnel completions through the checkout journey, this variation includes the any page in the Shop section prior to the start of the funnel journey.
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r shop_funnel_pre_start,fig.align='center',echo=FALSE}

shop_pre_post_start_funnel

```



#### Sales & Revenue

Here is the individual trends for each metric in the shop funnel.

##### Revenue:

```{r shop_revenue, fig.align='center',echo=FALSE, fig.height=5, fig.width=7}

ggplotly(shop_revenue)

```

##### Shop Orders:  

Shop - Order Step 4 - Order Confirmation (Serialized) (ev182)
```{r shop_orders, echo=FALSE, fig.align='center',fig.height=5, fig.width=7}

ggplotly(shop_orders)

```


#### Metrics

Here is the individual trends for shop sales.
Add Revenue events too.

```{r shop_metrics, fig.align='center',echo=FALSE}
# Anomaly Plots for each journey with Ribbon and Pre/Post separations
shop_events

```

#### Flows
Shop conversions by Channel. Start: **`r previous_week_7_start` to `r previous_week_7_end`**. 

```{r shop_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}

shop_conv_scatter_plot  
shop_conv_flow_plot

```


#### Change Point {.unlisted .unnumbered}

This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_shop@cpts[1]`**.

```{r shop_changepoints, echo=FALSE, fig.height=5, fig.width=7}

plot(fit_changepoint_shop)

```




### {.unlisted .unnumbered}

### Donate {.tabset}

Insights:

#### Summary


#### Funnels

**Week on Week performance**

Donation funnel completions through the checkout journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r donate_funnel_pre_post, fig.align='center',echo=FALSE}

donate_pre_post_funnel

```


#### Sales & Revenue




#### Metrics



#### Flows
Donate conversions by Channel. Start: **`r previous_week_7_start` to `r previous_week_7_end`**. 

```{r donate_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}

donate_conv_scatter_plot  
donate_conv_flow_plot

```


#### Change Point {.unlisted .unnumbered}
This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_donate@cpts[1]`**.

```{r donate_changepoints, echo=FALSE,fig.height=5, fig.width=7}

plot(fit_changepoint_donate)

```




### {.unlisted .unnumbered}
