
### Membership {.tabset}

Insights:

#### Summary


```{r insights_membership, echo=FALSE}

journey_name.insight <- "Commercial: Membership Checkout Steps 1-4" # No Spike Data
journey.insight <- get_insights(journey_name.insight)

```

Insight for Journey: **`r journey.insight$journey_name`**

* **[Min]**         The lowest amount of Visits was **`r journey.insight$min.Visits`** observed on **`r format(journey.insight$min.Visits.Date.Name, "%d %b")`**.  

* **[Average]**     This was **`r journey.insight$min.avg.diff`%** less than the average of **`r journey.insight$avg.Visits`**.  

* **[Max]**         During this period, the amount of Visits peaked at **`r journey.insight$max.Visits`** on **`r format(journey.insight$max.Visits.Date.Name, "%d %b")`**.

* **[Spike]**       The most recent peak in Visits increased notably on **`r format(journey.insight$Day, "%d %b")`**, where a significant peak of **`r journey.insight$Visits`** Visits was observed.  

* **[Trend]**       Throughout the duration of the analysis period, the overall trend has been **`r journey.insight$trend.slope.correlation`**. In the previous week the trend was **`r journey.insight$correlation.14`** over the last 7 days the trend has been **`r journey.insight$correlation.7`**. This is a **`r journey.insight$trend.change.relative`%** difference from the previous week.



#### Funnels
**Week on Week performance**

Membership funnel completions through the journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r membership_funnel_pre_post, echo=FALSE}
#library(plotly)
  membership_pre_post_funnel 

```

**Week on Week performance**

Membership funnel completions through the checkout journey, this variation includes the Join Us page prior to the start of the Membership funnel journey.  
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  


```{r membership_funnel_pre_start,fig.align='center',echo=FALSE}

membership_pre_post_start_funnel

```


#### Sales & Revenue

Metric: Membership Revenue (ev5) (event5)

##### Revenue:

```{r membership_revenue, fig.align='center',echo=FALSE, fig.height=5, fig.width=7}

ggplotly(membership_revenue)

```

##### Sales: 

Metric: Membership Step 4.0 - Confirmation (Serialized) (ev26) (event26)

```{r membership_sales, echo=FALSE, fig.align='center',fig.height=5, fig.width=7}

ggplotly(membership_sales)

```


#### Metrics

```{r membership_metrics, fig.align='center',echo=FALSE}

membership_events

```


#### Flows

Membership conversions by Channel. Start: **`r previous_week_7_start` to `r previous_week_7_end`**. 

```{r membership_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}
membership_conv_scatter_plot  
membership_conv_flow_plot
```


#### Change Point {.unlisted .unnumbered}

This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_membership@cpts[1]`**.

```{r membership_changepoints, echo=FALSE, fig.height=5, fig.width=7}

plot(fit_changepoint_membership)

```

### {.unlisted .unnumbered}


### Renewals {.tabset}

Insights:

#### Summary

```{r insights_renewals, echo=FALSE}

journey_name.insight <- "Commercial: Renew Checkout Steps 1-3" # No Spike Data
journey.insight <- get_insights(journey_name.insight)

```

Insight for Journey: **`r journey.insight$journey_name`**

* **[Min]**         The lowest amount of Visits was **`r journey.insight$min.Visits`** observed on **`r format(journey.insight$min.Visits.Date.Name, "%d %b")`**.  

* **[Average]**     This was **`r journey.insight$min.avg.diff`%** less than the average of **`r journey.insight$avg.Visits`**.  

* **[Max]**         During this period, the amount of Visits peaked at **`r journey.insight$max.Visits`** on **`r format(journey.insight$max.Visits.Date.Name, "%d %b")`**.

* **[Spike]**       The most recent peak in Visits increased notably on **`r format(journey.insight$Day, "%d %b")`**, where a significant peak of **`r journey.insight$Visits`** Visits was observed.  

* **[Trend]**       Throughout the duration of the analysis period, the overall trend has been **`r journey.insight$trend.slope.correlation`**. In the previous week the trend was **`r journey.insight$correlation.14`** over the last 7 days the trend has been **`r journey.insight$correlation.7`**. This is a **`r journey.insight$trend.change.relative`%** difference from the previous week.


#### Funnels

**Week on Week performance**

Renewal funnel completions through the journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r renew_funnel_pre, fig.align='center',echo=FALSE}

renew_pre_post_funnel

```

**Week on Week performance**

Renewal funnel completions through the checkout journey, this variation includes the Join or Renew page traffic prior to the start of the funnel journey.  
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r renew_funnel_pre_start,fig.align='center',echo=FALSE}

renew_pre_post_start_funnel

```


#### Sales & Revenue

##### Revenue:

Metric: Renew Revenue - Serialized (ev79) (event79)

```{r renew_revenue, fig.align='center',echo=FALSE, fig.height=5, fig.width=7}

ggplotly(renew_revenue)

```

##### Sales: 

Metric: Renew Step 3.0 - Confirmation - Serialized (ev76) (event76)

```{r renew_sales, echo=FALSE, fig.align='center',fig.height=5, fig.width=7}

ggplotly(renew_sales)

```

#### Metrics

```{r renewal_metrics, fig.align='center',echo=FALSE}

renewals_events

```


#### Flows
Renewals conversions by Channel. Start: **`r previous_week_7_start` to `r previous_week_7_end`**. 

```{r renewals_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}

membership_renewals_conv_scatter_plot  
membership_renewals_conv_flow_plot

```

#### Change Point {.unlisted .unnumbered}


This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_renew@cpts[1]`**.


```{r renew_changepoints, echo=FALSE, fig.height=5, fig.width=7}


plot(fit_changepoint_renew)


```

### {.unlisted .unnumbered}


### Holidays {.tabset}

Insights:

#### Summary

```{r insights_holidays, echo=FALSE}

journey_name.insight <- "Commercial: Holidays Checkout Steps 1-4" # No Spike Data
journey.insight <- get_insights(journey_name.insight)

```

Insight for Journey: **`r journey.insight$journey_name`**

* **[Min]**         The lowest amount of Visits was **`r journey.insight$min.Visits`** observed on **`r format(journey.insight$min.Visits.Date.Name, "%d %b")`**.  

* **[Average]**     This was **`r journey.insight$min.avg.diff`%** less than the average of **`r journey.insight$avg.Visits`**.  

* **[Max]**         During this period, the amount of Visits peaked at **`r journey.insight$max.Visits`** on **`r format(journey.insight$max.Visits.Date.Name, "%d %b")`**.

* **[Spike]**       The most recent peak in Visits increased notably on **`r format(journey.insight$Day, "%d %b")`**, where a significant peak of **`r journey.insight$Visits`** Visits was observed.  

* **[Trend]**       Throughout the duration of the analysis period, the overall trend has been **`r journey.insight$trend.slope.correlation`**. In the previous week the trend was **`r journey.insight$correlation.14`** over the last 7 days the trend has been **`r journey.insight$correlation.7`**. This is a **`r journey.insight$trend.change.relative`%** difference from the previous week.


#### Funnels

**Week on Week performance**

Holidays funnel completions through the journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  
 
```{r holidays_funnel_pre, fig.align='center',echo=FALSE}

holidays_pre_post_funnel

```

**Week on Week performance**

Holidays funnel completions through the checkout journey, this variation includes the any page in the Holidays section prior to the start of the funnel journey. 
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  


```{r holidays_funnel_post, fig.align='center',echo=FALSE}

holidays_pre_post_start_funnel
```


#### Sales & Revenue

Metric: Holidays Booking Total Revenue (Serialised) (ev125) (event125)

##### Revenue:

```{r holidays_revenue, fig.align='center',echo=FALSE, fig.height=5, fig.width=7}

ggplotly(holidays_revenue)

```

##### Sales: 

Metric: Holidays Booking Step 4.0 - Confirmation - Serialised (ev134) (event134)

```{r holidays_sales, echo=FALSE, fig.align='center',fig.height=5, fig.width=7}

ggplotly(holidays_sales)

```



#### Metrics

```{r holidays_metrics, fig.align='center',echo=FALSE}

holidays_events

```


#### Flows
```{r holidays_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}

holidays_conv_scatter_plot  
holidays_conv_flow_plot

```


#### Change Point {.unlisted .unnumbered}

This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_holidays@cpts[1]`**.

```{r holidays_changepoints, echo=FALSE, fig.height=5, fig.width=7}

plot(fit_changepoint_holidays)

```


### {.unlisted .unnumbered}


### Shop {.tabset}

Insights:

[Min] The lowest amount of Shop - Order Step 4 - Order Confirmation (Serialized) (ev182) was 15, which occurred on Feb. 3rd and was 84% less than the average of 92.

#### Summary

```{r insights_shop, echo=FALSE}

journey_name.insight <- "Commercial: Shop Checkout Steps 1-4" # No Spike Data
journey.insight <- get_insights(journey_name.insight)

```

Insight for Journey: **`r journey.insight$journey_name`**

* **[Min]**         The lowest amount of Visits was **`r journey.insight$min.Visits`** observed on **`r format(journey.insight$min.Visits.Date.Name, "%d %b")`**.  

* **[Average]**     This was **`r journey.insight$min.avg.diff`%** less than the average of **`r journey.insight$avg.Visits`**.  

* **[Max]**         During this period, the amount of Visits peaked at **`r journey.insight$max.Visits`** on **`r format(journey.insight$max.Visits.Date.Name, "%d %b")`**.

* **[Spike]**       The most recent peak in Visits increased notably on **`r format(journey.insight$Day, "%d %b")`**, where a significant peak of **`r journey.insight$Visits`** Visits was observed.  

* **[Trend]**       Throughout the duration of the analysis period, the overall trend has been **`r journey.insight$trend.slope.correlation`**. In the previous week the trend was **`r journey.insight$correlation.14`** over the last 7 days the trend has been **`r journey.insight$correlation.7`**. This is a **`r journey.insight$trend.change.relative`%** difference from the previous week.


#### Funnels

**Week on Week performance**

Shop funnel completions through the checkout journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r shop_funnel_pre, fig.align='center',echo=FALSE}

shop_pre_post_funnel

```

**Week on Week performance**

Shop funnel completions through the checkout journey, this variation includes the any page in the Shop section prior to the start of the funnel journey.
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r shop_funnel_pre_start,fig.align='center',echo=FALSE}

shop_pre_post_start_funnel

```



#### Sales & Revenue

Metric: Shop - Revenue

##### Revenue:

```{r shop_revenue, fig.align='center',echo=FALSE, fig.height=5, fig.width=7}

ggplotly(shop_revenue)

```

##### Shop Orders:  

Metric: Shop - Order Step 4 - Order Confirmation (Serialized) (ev182)

```{r shop_orders, echo=FALSE, fig.align='center',fig.height=5, fig.width=7}

ggplotly(shop_orders)

```


#### Metrics

Here is the individual trends for shop sales.
Add Revenue events too.

```{r shop_metrics, fig.align='center',echo=FALSE}
# Anomaly Plots for each journey with Ribbon and Pre/Post separations
shop_events

```

#### Flows
Shop conversions by Channel. Start: **`r previous_week_7_start` to `r previous_week_7_end`**. 

```{r shop_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}

shop_conv_scatter_plot  
shop_conv_flow_plot

```


#### Change Point {.unlisted .unnumbered}

This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_shop@cpts[1]`**.

```{r shop_changepoints, echo=FALSE, fig.height=5, fig.width=7}

plot(fit_changepoint_shop)

```




### {.unlisted .unnumbered}

### Donate {.tabset}

Insights:

#### Summary

```{r insights_donate, echo=FALSE}

journey_name.insight <- "Commercial: Donate Checkout Steps 1-2" # No Spike Data
journey.insight <- get_insights(journey_name.insight)

```

Insight for Journey: **`r journey.insight$journey_name`**

* **[Min]**         The lowest amount of Visits was **`r journey.insight$min.Visits`** observed on **`r format(journey.insight$min.Visits.Date.Name, "%d %b")`**.  

* **[Average]**     This was **`r journey.insight$min.avg.diff`%** less than the average of **`r journey.insight$avg.Visits`**.  

* **[Max]**         During this period, the amount of Visits peaked at **`r journey.insight$max.Visits`** on **`r format(journey.insight$max.Visits.Date.Name, "%d %b")`**.

* **[Spike]**       The most recent peak in Visits increased notably on **`r format(journey.insight$Day, "%d %b")`**, where a significant peak of **`r journey.insight$Visits`** Visits was observed.  

* **[Trend]**       Throughout the duration of the analysis period, the overall trend has been **`r journey.insight$trend.slope.correlation`**. In the previous week the trend was **`r journey.insight$correlation.14`** over the last 7 days the trend has been **`r journey.insight$correlation.7`**. This is a **`r journey.insight$trend.change.relative`%** difference from the previous week.


#### Funnels

**Week on Week performance**

Donation funnel completions through the checkout journey.   
Previous Week: **`r format(start_14_sun_start, "%d-%b")` to `r format(end_14_sun_end, "%d-%b")`**.  
Last 7 Days: **`r format(start_7_sun_start, "%d-%b")` to `r format(end_7_sun_end, "%d-%b")`**.

Hover over for fallout details at each stage.  

```{r donate_funnel_pre_post, fig.align='center',echo=FALSE}

donate_pre_post_funnel

```


#### Sales & Revenue:

Metric: Donate Revenue (Serialized) (ev114) (event114)

##### Revenue:
```{r donate_revenue, fig.align='center',echo=FALSE, fig.height=5, fig.width=7}

ggplotly(donate_revenue)

```

##### Sales: 

Metric: Donate Step 2.0 - Complete (Serialized) (ev116) (event116)

```{r donate_sales, echo=FALSE, fig.align='center',fig.height=5, fig.width=7}

ggplotly(donate_sales)

```


#### Metrics

```{r donate_metrics, fig.align='center',echo=FALSE}

donate_events

```


#### Flows
Donate conversions by Channel. Start: **`r previous_week_7_start` to `r previous_week_7_end`**. 

```{r donate_flow_scatter_plot, echo=FALSE, fig.align='center', fig.height=7, fig.width=9, warning=FALSE}

donate_conv_scatter_plot  
donate_conv_flow_plot

```


#### Change Point {.unlisted .unnumbered}
This plot shows the change in the mean visits through the funnel over the series.  
Change point occurred on day: **`r fit_changepoint_donate@cpts[1]`**.

```{r donate_changepoints, echo=FALSE,fig.height=5, fig.width=7}

plot(fit_changepoint_donate)

```




### {.unlisted .unnumbered}
